\chapter*{Survey Instruments}
\label{surveyInstrument}

\paragraph * {Demographics}\mbox{} 
\begin{itemize}
\item Year in university [Freshman, Sophomore, Junior, Senior]
\item Gender [Male, Female, Other]
\item What is your reason for taking this class [interested, other]
\item What is your major?
\end{itemize}

\paragraph * {Attitudes towards Computer Science}\mbox{}
\begin{itemize}
\item I like to use Computer Science to solve problems.
\item Knowledge of computing will allow me to secure a good job.
\item I can learn to understand computing concepts.
\item My career goals do not require that I learn computing skills.
\item I can achieve good grades (C or better) in computing courses.
\item I do not like using computer science to solve problems.
\item I am confident that I can solve problems by using computer applications.
\item The challenge of solving problems using computer science appeals to me.
\item I am comfortable with learning computing concepts.
\item I would take additional Computer Science courses if I were given the opportunity.
\item I am confident about my abilities with regards to computer science.
\item I do think I can learn to understand computing concepts.
\end{itemize}

\paragraph *{Attitudes about Computational Thinking}\mbox{}
\begin{itemize}
\item I am good at solving a problem by thinking about similar problems I've solved before.
\item I have good research skills.
\item I am good at using online search tools.
\item I am persistent at solving puzzles or logic problems.
\item I know how to write computer programs.
\item I am good at building things.
\item I'm good at ignoring irrelevant details to solve a problem.
\item I know how to write a computer program to solve a problem.
\item I work well in teams.
\item I think about the ethical, legal, and social implications of computing.
\end{itemize}

\paragraph *{Computer Science Mentors and Role Models}\mbox{}
\begin{itemize}
\item Before I came to UC Berkeley, I knew people who have careers in Computer Science.
\item There are people with careers in Computer Science who look like me.
\item I have role models within the Computer Science field that look like me.
\end{itemize}

\paragraph *{Identity and Self Efficacy}\mbox{}
\begin{itemize}
\item In this class, I feel I belong.
\item In this class, I feel awkward and out of place 
\item In this class, I feel like my ideas count
\item In this class, I feel like I matter.
\item I am comfortable interacting with peers from different backgrounds than my own (based on race, sexuality, etc.)
\item  I have good cultural competence, or the ability to interact effectively with people from diverse backgrounds.
\item Our class materials (e.g., case studies and projects) were relevant and practical
\end{itemize}

\paragraph *{Gendered Belief about Computer Science Ability}\mbox{}
\begin{itemize}
\item Women are less capable of success in CS than men
\item Men have better math and science abilities than women.
\item Women are smarter than men.
\end{itemize}

\paragraph *{Pre-Collegiate CS Preparation}\mbox{}
\begin{itemize}
\item Did you take a CS course in High School?
\item Did you have exposure to Computer Science before UC Berkeley?
\item Did a family member introduce you to Computer Science?
\item Did you have a close family member who is a Computer Scientist or is affiliated with computing industry?
\item Did your school offer AP CS?
\item How prepared did you feel about this class before it started?
\item Will you be taking any more CS classes (if so which ones?)
\item (For 61A only) Have you taken CS10, The Beauty and Joy of Computing?
\end{itemize}